Hierarchical Bayesian regression modelling predicts biochemical rection energies and facilitates quantitative modelling of cell metabolism

### 2023-10-27 paper/main.qmd
Update paper

Maud’s measurement model considers three types of measurement: metabolite
concentration measurements, enzyme concentration measurements and flux
measurements, represented by vectors $𝑦_{𝑐𝑜𝑛𝑐}$ $𝑦_{𝑒𝑛𝑧}$ and $𝑦_{𝑓𝑙𝑢𝑥}$
respectively.

@@

Metabolite and enzyme measurements are intended to represent the results of
quantitative metabolomics and proteomics experiments. The likelihood functions
for such measurements are shown in equations Equation 6 and Equation 7.

EQUATIONS

@@

Flux measurements, representing the results of quantitative fluxomics analyses,
are modelled using a likelihood function from a standard linear regression
model, as shown in equation 8 (REFERENCE). Flux measurements can be obtained
from the results of isotope labelling experiments using metabolic flux analysis,
for example as described in (Young 2014). When entering flux measurements,
it is important only to specify measurements for a network’s free fluxes, as
the values of some steady state fluxes in a metabolic network are constrained
by others, with the result that dependent fluxes cannot typically be measured
separately. If measurements of multiple dependent fluxes are entered,
information will inappropriately be double counted.

EQUATION

>>>>

Maud’s measurement model considers three types of measurement: metabolite
concentration measurements, enzyme concentration measurements and flux
measurements, represented by vectors $𝑦^{𝑐𝑜𝑛𝑐}$ $𝑦^{𝑒𝑛𝑧}$ and $𝑦^{𝑓𝑙𝑢𝑥}$
respectively.

@@

Metabolite and enzyme measurements are intended to represent the results of
quantitative metabolomics and proteomics experiments. The likelihood functions
for such measurements are shown in equations Equation \eqref{eq-yconc} and
Equation \eqref{eq-yenz}.

\begin{equation}
y_i^{conc} \sim LN(\ln{\hat{y}_i^{conc}}, \sigma_i^{conc})\label{eq-yconc}
\end{equation}

\begin{equation}
y_i^{enz} \sim LN(\ln{\hat{y}_i^{enz}}, \sigma_i^{enz})\label{eq-yenz}
\end{equation}

@@

Flux measurements, representing the results of quantitative fluxomics analyses,
are modelled using a likelihood function from a standard linear regression
model, as shown in equation \eqref{eq-yflux}. Flux measurements can be obtained
from the results of isotope labelling experiments using metabolic flux analysis,
for example as described in (Young 2014). When entering flux measurements,
it is important only to specify measurements for a network’s free fluxes, as
the values of some steady state fluxes in a metabolic network are constrained
by others, with the result that dependent fluxes cannot typically be measured
separately. If measurements of multiple dependent fluxes are entered,
information will inappropriately be double counted.

\begin{equation}
y_i^{flux} \sim LN(\ln{\hat{y}_i^{flux}}, \sigma_i^{flux})\label{eq-yflux}
\end{equation}

### 2023-10-27 paper/main.tex
Update paper

\title[]{Hierarchical Bayesian regression modelling predicts biochemical
rection energies and facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Below, we review the existing options in this
area, explain how Maud improves on the state of the art, describe the
intended modelling workflow and illustrate its use with an example
application.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, frame hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Maud's measurement model considers three types of measurement:
metabolite concentration measurements, enzyme concentration measurements
and flux measurements, represented by vectors \(𝑦_{𝑐𝑜𝑛𝑐}\) \(𝑦_{𝑒𝑛𝑧}\)
and \(𝑦_{𝑓𝑙𝑢𝑥}\) respectively.

@@

Metabolite and enzyme measurements are intended to represent the results
of quantitative metabolomics and proteomics experiments. The likelihood
functions for such measurements are shown in equations Equation\,6 and
Equation\,7.

EQUATIONS

@@

Flux measurements, representing the results of quantitative fluxomics
analyses, are modelled using a likelihood function from a standard
linear regression model, as shown in equation\,8 (REFERENCE). Flux
measurements can be obtained from the results of isotope labelling
experiments using metabolic flux analysis, for example as described in
(Young 2014). When entering flux measurements, it is important only to
specify measurements for a network's free fluxes, as the values of some
steady state fluxes in a metabolic network are constrained by others,
with the result that dependent fluxes cannot typically be measured
separately. If measurements of multiple dependent fluxes are entered,
information will inappropriately be double counted.

EQUATION

>>>>

\title[]{Hierarchical Bayesian regression modelling predicts biochemical
rection energies and facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Below, we review the existing options in this
area, explain how Maud improves on the state of the art, describe the
intended modelling workflow and illustrate its use with an example
application.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

Maud's measurement model considers three types of measurement:
metabolite concentration measurements, enzyme concentration measurements
and flux measurements, represented by vectors \(𝑦^{𝑐𝑜𝑛𝑐}\) \(𝑦^{𝑒𝑛𝑧}\)
and \(𝑦^{𝑓𝑙𝑢𝑥}\) respectively.

@@

Metabolite and enzyme measurements are intended to represent the results
of quantitative metabolomics and proteomics experiments. The likelihood
functions for such measurements are shown in equations
Equation\,\eqref{eq-yconc} and Equation\,\eqref{eq-yenz}.

\begin{equation}
y_i^{conc} \sim LN(\ln{\hat{y}_i^{conc}}, \sigma_i^{conc})\label{eq-yconc}
\end{equation}

\begin{equation}
y_i^{enz} \sim LN(\ln{\hat{y}_i^{enz}}, \sigma_i^{enz})\label{eq-yenz}
\end{equation}

@@

Flux measurements, representing the results of quantitative fluxomics
analyses, are modelled using a likelihood function from a standard
linear regression model, as shown in equation\,\eqref{eq-yflux}. Flux
measurements can be obtained from the results of isotope labelling
experiments using metabolic flux analysis, for example as described in
(Young 2014). When entering flux measurements, it is important only to
specify measurements for a network's free fluxes, as the values of some
steady state fluxes in a metabolic network are constrained by others,
with the result that dependent fluxes cannot typically be measured
separately. If measurements of multiple dependent fluxes are entered,
information will inappropriately be double counted.

\begin{equation}
y_i^{flux} \sim LN(\ln{\hat{y}_i^{flux}}, \sigma_i^{flux})\label{eq-yflux}
\end{equation}
